\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}

% Color Definitions
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\usepackage[T1]{fontenc}
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large 
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
      \textit{#3} & {\color{dark-grey} \small #4}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey} \small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Aditya More} \\ \vspace{5pt}
    \small AI Engineer $|$ Computer Vision $|$ Generative AI $|$ LLM Systems $|$ Deep Learning $|$ PyTorch $|$ MLOps\\ \vspace{5pt}
    \faPhone* \texttt{+91 7058067035} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{adityadmore2000@gmail.com} \hspace{1pt} $|$ 
    \hspace{1pt} \faLinkedin \hspace{2pt} \href{https://www.linkedin.com/in/adityamore2k/}{\texttt{adityamore2k}} \hspace{1pt} $|$
    \hspace{1pt} \faGithub \hspace{2pt} \href{https://github.com/adityadmore2000/}{\texttt{adityadmore2000}}
    \\ \vspace{2pt}
    \small Pune, India
\end{center}

%-----------PROFILE-----------
\section{SUMMARY}
\small{AI/ML Engineer experienced in building deep learning, computer vision, and generative AI systems using Python and PyTorch. Worked on real-time computer vision pipelines, model training, inference optimization, and production-oriented AI workflows across surveillance analytics and LLM-based systems. Experienced in AI deployment workflows, model evaluation, and frontend-integrated AI applications using React-based technologies.}
%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
{Software Engineering Intern $|$ NDSoftTech Solutions}{03/2026 - 05/2026}
{NDSS Internship}{Pune, India}

\resumeItemListStart

\resumeItem{Developed and integrated production-oriented mobile application features using \textbf{React Native}, Firebase, and API-driven workflows across profile, wallet, rewards, and authentication systems.}

\resumeItem{Implemented reusable UI architectures, structured loading states, optimistic updates, and frontend state synchronization to improve application responsiveness and user experience.}

\resumeItem{Worked on media upload workflows, profile systems, and API-integrated frontend features involving asynchronous state handling and backend-connected user flows.}

\resumeItem{Collaborated using \textbf{Git/GitHub} workflows including pull requests, merge conflict resolution, local debugging, and feature integration across shared codebases.}

\resumeItem{Used AI-assisted development workflows involving design-to-code tooling, rapid UI prototyping, debugging, and iterative feature implementation across mobile application modules.}

\resumeItemListEnd

\resumeSubheading
  {AI Engineer $|$ Freelancer}{07/2024 - 03/2026}
  {Computer Vision \& Generative AI Systems Development}{}
  \resumeItemListStart
  \resumeItem{Developed AI monitoring and warehouse parcel tampering detection systems using YOLO-based real-time video inference workflows for PPE compliance, worker/vehicle tracking, restricted-zone intrusion alerts, and surveillance analytics.}
\resumeItem{Achieved 92.7\% precision, 95.0\% recall, and 97.4\% mAP50 on parcel-condition detection workflows using YOLO-based computer vision models.}

    \resumeItem{Implemented event-driven monitoring logic including line-crossing analytics, zone-based alerts, tracking-ID association, OCR-assisted metadata extraction, and rule-based incident triggering across surveillance pipelines.}

    \resumeItem{Worked on drone-imagery-based agricultural monitoring systems involving vegetation analysis, weed-region detection, orchard yield estimation, and field-level analytics using lightweight segmentation and detection models.}

    \resumeItem{Built production-oriented hybrid LLM systems using \textbf{OpenAI API}, \textbf{Ollama}, and Python, enabling fallback routing, offline-first execution, cost optimization, and improved inference reliability.}

    \resumeItem{Engineered an offline voice-to-voice LLM system using \textbf{LiveKit}, \textbf{LlamaIndex}, and locally hosted models, obtaining a real-time conversational AI}

    \resumeItem{Designed orchestrated AI workflows integrating speech-to-text, retrieval, LLM reasoning, and text-to-speech components, improving system control, response reliability, and offline execution capabilities.}

    \resumeItem{Implemented \textbf{RAG} workflows using vector embeddings, semantic search, and \textbf{LlamaIndex} for context-aware responses over structured document corpora.}

    \resumeItem{Built containerized inference workflows using \textbf{Docker}, local GPU execution, and reproducible deployment pipelines for efficient model serving and offline inference.}

    \resumeItem{Developed modular AI reasoning workflows using structured outputs, deterministic verification with \textbf{SymPy}, retry-aware execution, and multi-stage orchestration for improved reliability.}

    \resumeItem{Implemented reproducible MLOps workflows using MLflow and DVC-friendly dataset/version management for experiment tracking, model evaluation, hyperparameter tuning, and artifact comparison across YOLO-based surveillance analytics pipelines.}

    \resumeItem{Performed deployment-oriented experimentation involving confidence-threshold calibration, inference optimization, confusion-matrix analysis, and false-positive reduction using negative-sample refinement strategies.}
  \resumeItemListEnd

\resumeSubheading
  {AI/ML Engineer $|$ Neilsoft}{07/2023 - 07/2024}
  {Computer Vision Engineering}{Pune, India}
  \resumeItemListStart

    \resumeItem{Developed and integrated Computer Vision pipelines using \textbf{YOLOv5}, \textbf{YOLOX}, \textbf{YOLOv8}, and \textbf{PyTorch} for object detection and instance segmentation across architectural, structural, and MEP domains, improving inference reliability and production deployment readiness.}

    \resumeItem{Engineered scalable model development workflows using large-scale domain-specific datasets with \textbf{1300+ training images}, including preprocessing, annotation validation, augmentation strategies, COCO conversion, and precision optimization across \textbf{15+ object classes}.}

    \resumeItem{Delivered production-ready detection models achieving up to \textbf{83.4 mAP} for ARCH, \textbf{85.1 mAP} for MEP, and stable validation performance of \textbf{0.54 COCO AP50--95}, improving detection quality across architectural and MEP systems.}

    \resumeItem{Performed precision--recall benchmarking across YOLOX and YOLOv8 for ladder and staircase detection, where YOLOX achieved higher precision (\textbf{81.67 AP}) while YOLOv8 delivered stronger recall (\textbf{100\%}), supporting architecture-specific deployment decisions based on use-case requirements.}

    \resumeItem{Used \textbf{Pandas} for dataset and annotation analysis, identifying class imbalance and over-annotated samples to improve dataset quality and training reliability.}
    
    \resumeItem{Set up and debugged point cloud segmentation frameworks including \textbf{SoftGroup}, \textbf{RepSurf}, and PointGroup, resolving environment and dependency issues, and supported comparative evaluation of approaches for domain-specific use cases.}
    
  \resumeItemListEnd  
\resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{PROJECTS}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Math Mentor AI} $|$ \emph{LLM + Tool-Based Reasoning System}}{}
\resumeItemListStart
\resumeItem{Experimented with open-source reasoning models using \textbf{Hugging Face Transformers}, evaluating mathematical reasoning performance and reliability limitations in LLM-based problem solving.}

\resumeItem{Built an end-to-end math reasoning pipeline combining LLM-generated reasoning with deterministic verification using \textbf{SymPy}.}

\resumeItem{Designed modular AI workflows integrating structured outputs, deterministic verification, retry-aware execution, and multi-stage orchestration for improved reliability.}

\resumeItem{Implemented validation and normalization workflows for AI-generated outputs using deterministic verification and retry-aware response handling.}

\resumeItemListEnd

\resumeProjectHeading
{\textbf{Offline Voice-to-Voice AI Assistant} $|$ \emph{LiveKit, LlamaIndex, Docker}}{}
\resumeItemListStart
\resumeItem{Developed a real-time voice-based AI assistant using locally hosted LLMs, enabling end-to-end offline conversational interaction.}
\resumeItem{Implemented retrieval-augmented generation (RAG) pipelines using vector embeddings and semantic search, improving contextual relevance and response accuracy for knowledge-based queries.}
\resumeItem{Designed a streaming pipeline for speech input/output and LLM inference, optimizing latency and interaction smoothness.}
\resumeItem{Containerized local inference workflows using \textbf{Docker} and GPU-backed execution for reproducible offline deployment and low-latency conversational interaction.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Warehouse Parcel Monitoring \& Video Analytics System} $|$ \emph{YOLO, PyTorch, FastAPI, MLflow}}{}
\resumeItemListStart
\resumeItem{Developed a modular warehouse surveillance analytics pipeline for parcel-condition monitoring and investigation-oriented CCTV review workflows using YOLO-based video inference.}

\resumeItem{Implemented object detection, lightweight tracking-ID association, line-crossing analytics, OCR-assisted metadata extraction, and rule-based event triggering across sampled video streams.
}

\resumeItem{Built structured evidence extraction workflows for parcel movement history, timestamp-linked handling events, and condition-based incident review from CCTV footage.
}

\resumeItem{Achieved \textbf{92.7\%} precision, \textbf{95.0\%} recall, and \textbf{97.4\%} mAP50 on parcel-condition detection workflows using YOLO-based computer vision models.
}

\resumeItem{Integrated MLflow-based experiment tracking and DVC-friendly dataset/version management for reproducible training, evaluation, artifact comparison, and inference analysis workflows.
}

\resumeItem{Redesigned the pipeline into a multi-stage architecture separating warehouse parcel localization and tamper-condition analysis after identifying domain-shift and small-object limitations during real CCTV inference.}

\resumeItemListEnd

\resumeSubHeadingListEnd
%-----------SKILLS-----------
\section{SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{

\textbf{Programming \& Frameworks:} {Python, FastAPI, Pandas, NumPy, Hugging Face Transformers} \\

\textbf{Machine Learning \& Computer Vision:} {PyTorch, Deep Learning, Computer Vision, YOLOv5, YOLOX, YOLOv8, Object Detection, Instance Segmentation, Image Classification, Model Training, Model Evaluation, Dataset Engineering, Data Preprocessing} \\

\textbf{Generative AI \& LLM Systems:} {LLMs, OpenAI API, Ollama, LlamaIndex, RAG, Semantic Search, Vector Embeddings, Prompt Engineering, Structured Outputs, Tool Calling, Multi-Agent Workflows} \\

\textbf{Deployment \& Infrastructure:} {Docker, MLflow, DVC, CUDA, GPU-Based Training, Experiment Tracking, Model Evaluation, Batch Inference, API-Based Model Serving, Runtime Optimization} \\

\textbf{Additional Exposure:} {ONNX Model Export, OCR Workflows, Torchserve, Git/GitHub}
}}
\end{itemize}
%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Marathwada Mitra Mandal’s Institute of Technology}{Pune, India}
      {Bachelor of Engineering (B.E) in Computer Engineering}{July 2023}

\end{document}